Certified Symbolic Finite Transducers: Formalization and Applications to String Analysis

### 2025-11-25 Paper/SFT.tex
fix reviews

\begin{definition}[Symbolic Finite Transducer]
\label{def-sft}
   A Symbolic Finite Transducer over $\tau_1\rightarrow \tau_2$ is a quadruple $\mathcal{T} = (\mathcal{Q}, \Delta, \mathcal{I}, \mathcal{F})$, where 
   \begin{itemize}
   \item $\mathcal{Q}$ is a finite set of states,
   \item $\mathcal{I}\subseteq \mathcal{Q}$ is the set of initial states,
   \item $\mathcal{F} \subseteq\mathcal{Q}$ is the set of accepting states,
   \item $\Delta$ is the set of transition relations. Each element in $\Delta$ is of the form $(q, \phi, f, q')$ or written as $q\xrightarrow{\phi, f} q'$, where $q$ and $q'$ are states in $\mathcal{Q}$.
   $\phi$ is a predicate of type $\tau_1\rightarrow \mathbb{B}$.
   $f$ is a lambda term of type $\tau_1\rightarrow \tau_2$. $f$ is called an \emph{output function}.
   \end{itemize}

>>>>

\begin{definition}[Symbolic Finite Transducer]
\label{def-sft}
   A Symbolic Finite Transducer over $\tau_1\rightarrow \tau_2$ is a quadruple $\mathcal{T} = (\mathcal{Q}, \Delta, \mathcal{I}, \mathcal{F})$, where 
   \begin{itemize}
   \item $\mathcal{Q}$ is a finite set of states,
   \item $\mathcal{I}\subseteq \mathcal{Q}$ is the set of initial states,
   \item $\mathcal{F} \subseteq\mathcal{Q}$ is the set of accepting states,
   \item $\Delta$ is the set of transition relations. Each element in $\Delta$ is of the form $(q, \phi, f, q')$ or written as $q\xrightarrow{\phi, f} q'$, where $q$ and $q'$ are states in $\mathcal{Q}$,
   $\phi$ is a predicate of type $\tau_1\rightarrow \mathbb{B}$,
   $f$ is a lambda term of type $\tau_1\rightarrow \tau_2$, and $f$ is called an \emph{output function}.
   \end{itemize}

### 2025-11-25 Paper/formalization.tex
fix reviews

Firstly, $'a \text{ set option }$ is the input type of the transition, it accepts a set of elements of type $'a$ or $\texttt{None}$ corresponding to empty string $\varepsilon$. 
Accepting a set of $'a$ elements aims to express the same but more abstract semantics of the input labels in Definition \ref{def-sft}, in which an input label is a predicate. A predicate's semantics as introduced before represents a set of elements that make the predicate true. But predicates have various different forms. For instance, the interval $[1-9]$ represents the set $\{e \mid 1 \leq e \leq 9\}$. The predicate $\lambda b.~ b[7] = 1$, where $b$ is a bit vector of length 8, denotes the set of bit vectors that have a 1 in the 7th position. All different forms of labels are abstracted as sets in our formalization.
%
The value $\texttt{None}$ represents the empty string $\varepsilon$ in our formalization, indicating a transition that consumes no input but may still produce output elements. This design choice facilitates the modeling of real-world applications in SFTs, as we will demonstrate in our application to string solvers.

The second element of type $'i$ in LTTS serves as an index into the output function space. 
%
We use indices instead of functions %themselves 
to enable the reuse of the same output functions for different transitions.
%
The mapping $\mathcal{M}_t$ associates each index with a specific output
function. These output functions, formalized by \texttt{Tlabel}, map a single
input element to a set of possible output elements rather than to a single
element. This design enables nondeterministic output behavior, where the
transducer may select any element from the output set arbitrarily or according
to specified criteria. Further, output functions can produce empty string $\varepsilon$ by returning $\texttt{None}$, providing further flexibility in transition behavior.

@@

type_synonym |$('q, 'a)$| LTS = "|$'q \times 'a \text{ set }\times 'q$|"    
	\end{lstlisting}
\caption{The formalization of $\varepsilon$SFAs and SFAs}
\label{fig-def-FAs}
\end{figure}

@@

\begin{figure}[hbt!]
	\begin{lstlisting}
definition productT :: |$"('q,'a,'i,'b)"$| NFT |$\Rightarrow$| 
   |$('q,'a)$| NFA |$\Rightarrow$||$(('a,'b)$| Tlabel |$\Rightarrow 'a \text{ set}$| 
   |$\Rightarrow 'b\text{ set option})\Rightarrow$| |$('q\times 'q, ~'b)$| eNFA where
"productT |$\mathcal{T}$| |$\mathcal{A}$| F = |$\llparenthesis$|
  |$\mathcal{Q}e = \mathcal{Q}_t~\mathcal{T} \times \mathcal{Q} ~\mathcal{A}$|,
  |$\Delta_e = \{((p,p'),~\texttt{the }(((\mathcal{M}_t~\mathcal{T})~f)\texttt{ None}),~(q, p'))\mid $|
       |$p, p', q, f.~p'\in \mathcal{Q}~\mathcal{A}~\land$| |$(p, (\texttt{None}, f), q)\in \Delta_t~\mathcal{T}$|
        |$ \land~\exists S.~(\mathcal{M}_t~\mathcal{T})~f~\texttt{None} = \text{Some } S\} ~\cup$|
      |$\{((p,p'),~\texttt{the }(F~((\mathcal{M}_t~\mathcal{T})~f)~(\sigma_1\cap\sigma_2)),(q, q'))\mid $|
       |$p, p', q, \sigma_1, \sigma_2, q', f.~(p, (\text{Some }\sigma_1, f), q)\in \Delta_t~\mathcal{T} \land$|
       |$ (p', \sigma_2, q')\in\Delta~\mathcal{A}\land \sigma_1\cap \sigma_2 \neq \emptyset~\land$|
          |$ \exists S.~F~((\mathcal{M}_t~\mathcal{T})~f)~(\sigma_1\cap\sigma_2) = \text{Some } S\}$|,
  |$\Delta_e' = \{((p,p'),~(q, p'))\mid p, p', q, f.~p'\in \mathcal{Q}~\mathcal{A} \land$|
       |$(p, (None, f), q)\in \Delta_t~\mathcal{T}~\land $|
       |$(\mathcal{M}_t~\mathcal{T})~f~\texttt{None} = \text{None}\} ~\cup$|
      |$\{((p,p'),~(q, q'))\mid p, p', q, \sigma_1, \sigma_2, q', f.~$|
        |$ (p, (\text{Some }\sigma_1, f), q)\in \Delta_t~\mathcal{T} \land (p', \sigma_2, q')\in\Delta~\mathcal{A}$|
        |$\land~\sigma_1\cap \sigma_2 \neq \emptyset~\land\exists x\in(\sigma_1\cap\sigma_2).$|
        |$~((\mathcal{M}_t~\mathcal{T})~f)~(\text{Some } x) = \text{None} \}$|,
  |$\mathcal{I}_e = \mathcal{I}_t~\mathcal{T} \times \mathcal{I}~\mathcal{A}$|
  |$\mathcal{F}_e = \mathcal{F}_t~\mathcal{T} \times \mathcal{F}~\mathcal{A}$| |$\rrparenthesis$|"
	\end{lstlisting}
\caption{The formalization of product operation}
\label{fig-def-FTProd}
\end{figure}

@@

\[\texttt{F}~f~A=\texttt{Some } (\bigcup_{a\in A} (\text{if }f~a= \text{Some }S \texttt{ then } S \texttt{ else } \emptyset))\].

@@

\begin{figure}[hbt!]
	\begin{lstlisting}
lemma productT_correct:
  fixes |$\mathcal{T}$| |$\mathcal{A}$| F
  assumes 
   F_ok1: "|$\forall~f~s.~(\forall e \in s.~f~(\text{Some } e) = \text{None})\longleftrightarrow$|
       |$\text{ F}~f~s = \text{None}"$|
   and F_ok2: "|$\forall~f~s.~ \texttt{F}~f~s\neq \texttt{None} \longrightarrow$| F |$f~s$| = 
        |$\text{Some }(\cup~\{\texttt{S} \mid e~\texttt{S}.~e \in s~\land~$|
        |$f~(\text{Some }e) = \text{ Some S}\})$|"
      and wfTA: "NFT_wf |$\mathcal{T}~\land \text{ NFA } \mathcal{A}$|"
  |$\textcolor{blue}{\text{shows}}$| "|$\mathcal{L}_e$| (productT |$\mathcal{T}~\mathcal{A}$| F) = outputL 
          |$\mathcal{T}~\mathcal{A}$|"

@@

Figure \ref{fig-def-product-correct} presents Lemma \texttt{productT\_correct}, which establishes the correctness of the product operation. The lemma's assumptions, \texttt{F\_ok1} and \texttt{F\_ok2}, specify the essential properties of function \texttt{F}. 
The assumptions $\texttt{NFT\_wf}~\mathcal{T}$ and $\texttt{NFA}~\mathcal{A}$ ensure that the SFT $\mathcal{T}$ and the SFA $\mathcal{A}$ are well-formed.
The conclusion, marked by \textcolor{blue}{\texttt{shows}}, demonstrates that the language of the constructed $\varepsilon$SFA ($\mathcal{L}_e$ denotes the language of $\varepsilon$SFA) from $\mathcal{T} \times \mathcal{A}$ coincides with the mathematical semantics defined by \texttt{outputL}, thereby establishing semantic preservation of the product construction.

>>>>

Firstly, $'a \text{ set option }$ is the input type (\texttt{option} type of set) of the transition, it accepts a set of elements of type $'a$ or $\texttt{None}$ corresponding to empty string $\varepsilon$. 
Accepting a set of $'a$ elements aims to express the same but more abstract semantics of the input labels in Definition \ref{def-sft}, in which an input label is a predicate. A predicate's semantics as introduced before represents a set of elements that make the predicate true. But predicates have various different forms. For instance, the interval $[1-9]$ represents the set $\{e \mid 1 \leq e \leq 9\}$. The predicate $\lambda b.~ b[7] = 1$, where $b$ is a bit vector of length 8, denotes the set of bit vectors that have a 1 in the 7th position. All different forms of labels are abstracted as sets in our formalization.
%
The value $\texttt{None}$ (empty string) facilitates the modeling of real-world applications in SFTs, as we will demonstrate in our application to string solvers.

The second element of type $'i$ in LTTS serves as an index into the output function space. 
%
We use indices instead of functions %themselves 
to enable the reuse of the same output functions for different transitions.
%
The mapping $\mathcal{M}_t$ associates each index with a specific output
function. These output functions, formalized by \texttt{Tlabel}, map a single
input element to a set of possible output elements to model nondeterministic output behavior, where the
transducer may select any element from the output set arbitrarily or according
to specified criteria. Further, output functions can produce empty string $\varepsilon$ by returning $\texttt{None}$, providing further flexibility in transition behavior.

@@

type_synonym |$('q, 'a)$| LTS =
          "|$'q~\times~'a \text{ set }\times ~'q$| set"
	\end{lstlisting}
\caption{The formalization of $\varepsilon$SFAs and SFAs}
\label{fig-def-FAs}
\end{figure}

@@

\begin{figure}[hbt!]
	\begin{lstlisting}
definition productT :: |$"('q,'a,'i,'b)"$| NFT |$\Rightarrow$|
   |$('q,'a)$| NFA |$\Rightarrow$||$(('a,'b)$| Tlabel |$\Rightarrow 'a \text{ set}$|
   |$\Rightarrow 'b\text{ set option})\Rightarrow$| |$('q\times 'q, ~'b)$| eNFA where
"productT |$\mathcal{T}$| |$\mathcal{A}$| F = |$\llparenthesis$|
  |$\mathcal{Q}e = \mathcal{Q}_t~\mathcal{T} \times \mathcal{Q} ~\mathcal{A}$|,
  |$\Delta_e =$| (* case of |$\epsilon$|-transitions *)
      |$\{((p,p'),~\texttt{the }(((\mathcal{M}_t~\mathcal{T})~f)\texttt{ None}),~(q, p'))\mid $|
       |$p, p', q, f.~p'\in \mathcal{Q}~\mathcal{A}~\land$| |$(p, (\texttt{None}, f), q)\in \Delta_t~\mathcal{T}$|
        |$ \land~\exists S.~(\mathcal{M}_t~\mathcal{T})~f~\texttt{None} = \text{Some } S\} ~\cup$|
      (* case of non-|$\epsilon$|-transitions *)
      |$\{((p,p'),~\texttt{the }(\texttt{F}~((\mathcal{M}_t~\mathcal{T})~f)~(\sigma_1\cap\sigma_2)),(q, q'))\mid $|
       |$p, p', q, \sigma_1, \sigma_2, q', f.~(p, (\text{Some }\sigma_1, f), q)\in \Delta_t~\mathcal{T} \land$|
       |$ (p', \sigma_2, q')\in\Delta~\mathcal{A}\land \sigma_1\cap \sigma_2 \neq \emptyset~\land$|
          |$ \exists S.~\texttt{F}~((\mathcal{M}_t~\mathcal{T})~f)~(\sigma_1\cap\sigma_2) = \text{Some } S\}$|,
  |$\Delta_e' =$| (* case of |$\epsilon$|-transitions *)
      |$\{((p,p'),~(q, p'))\mid p, p', q, f.~p'\in \mathcal{Q}~\mathcal{A} \land$|
       |$(p, (None, f), q)\in \Delta_t~\mathcal{T}~\land $|
       |$(\mathcal{M}_t~\mathcal{T})~f~\texttt{None} = \text{None}\} ~\cup$|
      (* case of non-|$\epsilon$|-transitions *)
      |$\{((p,p'),~(q, q'))\mid p, p', q, \sigma_1, \sigma_2, q', f.~$|
        |$ (p, (\text{Some }\sigma_1, f), q)\in \Delta_t~\mathcal{T} \land (p', \sigma_2, q')\in\Delta~\mathcal{A}$|
        |$\land~\sigma_1\cap \sigma_2 \neq \emptyset~\land\exists x\in(\sigma_1\cap\sigma_2).$|
        |$~((\mathcal{M}_t~\mathcal{T})~f)~(\text{Some } x) = \text{None} \}$|,
  |$\mathcal{I}_e = \mathcal{I}_t~\mathcal{T} \times \mathcal{I}~\mathcal{A}$|
  |$\mathcal{F}_e = \mathcal{F}_t~\mathcal{T} \times \mathcal{F}~\mathcal{A}$| |$\rrparenthesis$|"
	\end{lstlisting}
\caption{The formalization of product operation}
\label{fig-def-FTProd}
\end{figure}

@@

\[\texttt{F}~f~A=\texttt{Some } \bigcup_{a\in A} \text{if }f~a= \text{Some }S \texttt{ then } S \texttt{ else } \emptyset\].

@@

\begin{figure}[hbt!]
	\begin{lstlisting}
lemma productT_correct:
  fixes |$\mathcal{T}$| |$\mathcal{A}$| F
  assumes
   F_None: "|$\forall~f~s.~(\forall e \in s.~f~(\text{Some } e) = \text{None})\longleftrightarrow$|
       |$\text{ F}~f~s = \text{None}"$| and
   F_Some: "|$\forall~f~s.~ \texttt{F}~f~s\neq \texttt{None} \longrightarrow$| F |$f~s$| =
        |$\text{Some }(\cup~\{\texttt{S} \mid e~\texttt{S}.~e \in s~\land~$|
        |$f~(\text{Some }e) = \text{ Some S}\})$|"
      and wfTA: "NFT_wf |$\mathcal{T}~\land \text{ NFA } \mathcal{A}$|"
  |$\textcolor{blue}{\text{shows}}$| "|$\mathcal{L}_e$| (productT |$\mathcal{T}~\mathcal{A}$| F) = outputL
          |$\mathcal{T}~\mathcal{A}$|"

@@

Figure \ref{fig-def-product-correct} presents Lemma \texttt{productT\_correct}, which establishes the correctness of the product operation. The assumptions, \texttt{F\_None} and \texttt{F\_Some}, specify the essential properties of function \texttt{F}. 
The assumptions $\texttt{NFT\_wf}~\mathcal{T}$ and $\texttt{NFA}~\mathcal{A}$ ensure that the SFT $\mathcal{T}$ and the SFA $\mathcal{A}$ are well-formed.
The conclusion, marked by \textcolor{blue}{\texttt{shows}}, demonstrates that the language of the constructed $\varepsilon$SFA ($\mathcal{L}_e$ denotes the language of $\varepsilon$SFA) from $\mathcal{T} \times \mathcal{A}$ coincides with the mathematical semantics defined by \texttt{outputL}, thereby establishing semantic preservation of the product construction.

### 2025-11-25 Paper/introduction.tex
abstract and intro
fix reviews

Finite Automata (FA) and Finite Transducers (FT) are fundamental constructs in the theory of formal languages, with extensive applications in programming 
languages and software engineering. Despite this, many practical applications
that employ FAs and FTs --- for example, string analysis for web applications
%character sanitization in web
%applications 
(which easily prone to XSS vulnerabilities) and string constraint solving
--- require extremely large alphabets (e.g. UTF-16), which are beyond the
capabilities of classical automata algorithms
\cite{DV21,cav/DAntoniV17,uss/HooimeijerLMSV11,Berkeley-JavaScript}.
More precisely, explicit automata/transducer representations would yield 
an extremely large number of transitions (potentially, one for 
each letter).
%For example, recent advancements in string solvers, as demonstrated by \cite{pacmpl/ChenFHHHKLRW22}, have illustrated the relationship between regular expressions in modern programming languages and various forms of FAs and FTs. Additionally, FAs and FTs find significant industrial applications, such as in the verification of AWS access control policies \cite{DBLP:conf/fmcad/BackesBCDGLRTV18}.

@@

Symbolic Finite Automata (SFA) and Symbolic Finite Transducers (SFT)
\cite{cav/DAntoniV17, VeanesHLMB12Transducer,DV21} were proposed around 15 years ago
to deal with the alphabet-explosion problem that often arises in practical
applications. 
%represent advanced extensions of classic FAs and  FTs, enhancing their applicability in practical scenarios.
%
These symbolic extensions permit transition labels defined by an effective 
boolean algebra, allowing for a succinct representation of a set of transitions
that can be conveniently manipulated. 
%more expressive representations. 
For example, in the interval algebra, a transition label might be specified as 
an interval [$\texttt{a}-\texttt{z}$], encompassing all characters from
$\texttt{a}$ to $\texttt{z}$. As another example, in the SMT-Algebra
(particularly, of the theory of Linear Integer Arithmetic), %or 
one could associate an arithmetic condition ($x \mod 2 = 0$) to a transition, 
denoting all even numbers. Efficient algorithms for manipulating (e.g. computing
closures) and analyzing (e.g. checking emptiness) SFA and SFT are by now
rather mature (e.g see the CACM article \cite{DV21}).
SFA and SFT have been applied in numerous domains including analysis of web
applications against XSS vulnerabilities \cite{VeanesHLMB12Transducer,uss/HooimeijerLMSV11},
runtime behavior monitoring \cite{osdi/YaseenABCL20}, automated program
transformation \cite{pldi/HuD17}, and finally SMT solving for the unicode theory
of strings (e.g. see \cite{pacmpl/ChenFHHHKLRW22,CHL+19}).
%Furthermore, numerous studies have demonstrated the broad applicability of SFTs across diverse domains. The work of \cite{VeanesHLMB12Transducer} showcases SFTs in security-critical applications, particularly for cross-site scripting (XSS) prevention. \cite{uss/HooimeijerLMSV11} extends this security focus by applying SFTs to web application sanitizer analysis. In system verification, \cite{osdi/YaseenABCL20} employs SFTs for runtime behavior monitoring, while \cite{pldi/HuD17} demonstrates their utility in automated program transformation through systematic inversion techniques.
%This symbolic approach not only provides a more succinct representation but also supports infinite alphabets, thereby extending the expressive capabilities of FAs and FTs.

@@

Despite these, existing verified implementations for string analysis do not
handle the following indispensable string operations for analysis of web
applications (e.g. see
\cite{DBLP:conf/popl/LinB16,Kern,Berkeley-JavaScript,systematic-transduction,uss/HooimeijerLMSV11}):
\emph{string transductions} and \emph{replaceall} operators. In particular, 
string transductions are used frequently in web applications (e.g. for
sanitization, as well as implicitly applied transductions, for instance
through \texttt{innerHTML}) and are well-known to be critical for analyzing XSS
vulnerabilities for web applications
\cite{Berkeley-JavaScript,systematic-transduction,Kern,uss/HooimeijerLMSV11,DBLP:conf/popl/LinB16}. In particular, SMT-LIB string constraints that 
arise from such applications require the \emph{replaceall} operator, which is currently not handled by any existing verified
implementation. This paper tackles the formalization of SFA/SFT and
their associated algorithms, as well as applications to analysis of sanitizers
and verified solver for string constraints. 
%\textcolor{red}{Updated up to here
%so far}

>>>>

Finite Automata (FA) and Finite Transducers (FT) are fundamental constructs in the theory of formal languages, with extensive applications in programming 
languages and software engineering. Despite this, many practical applications
that employ FAs and FTs --- for example, string analysis for web applications
%character sanitization in web
%applications 
(which easily prone to XSS vulnerabilities) and string constraint solving
--- require extremely large alphabets (e.g. Unicode), which are beyond the
capabilities of classical automata algorithms
\cite{DV21,cav/DAntoniV17,uss/HooimeijerLMSV11,Berkeley-JavaScript}.
More precisely, explicit automata/transducer representations would yield 
an extremely large number of transitions (potentially, one for 
each letter).
%For example, recent advancements in string solvers, as demonstrated by \cite{pacmpl/ChenFHHHKLRW22}, have illustrated the relationship between regular expressions in modern programming languages and various forms of FAs and FTs. Additionally, FAs and FTs find significant industrial applications, such as in the verification of AWS access control policies \cite{DBLP:conf/fmcad/BackesBCDGLRTV18}.

@@

Symbolic Finite Automata (SFA) and Symbolic Finite Transducers (SFT)
\cite{cav/DAntoniV17, VeanesHLMB12Transducer,DV21} were proposed around 2010
to deal with the alphabet-explosion problem that often arises in practical
applications. 
%represent advanced extensions of classic FAs and  FTs, enhancing their applicability in practical scenarios.
%
These symbolic extensions permit transition labels defined by an effective 
boolean algebra, allowing for a succinct representation of a set of transitions
that can be conveniently manipulated. 
%more expressive representations. 
For example, in the interval algebra, a transition label might be specified as 
an interval [$\texttt{a}-\texttt{z}$], encompassing all characters from
$\texttt{a}$ to $\texttt{z}$. As another example, in the SMT-Algebra
(particularly, of the theory of Linear Integer Arithmetic), %or 
one could associate an arithmetic condition ($x \mod 2 = 0$) to a transition, 
denoting all even numbers. Efficient algorithms for manipulating (e.g. computing
closures) and analyzing (e.g. checking emptiness) SFA and SFT are by now
rather mature (e.g see the CACM article \cite{DV21}).
SFA and SFT have been applied in numerous domains including analysis of web
applications against XSS vulnerabilities \cite{VeanesHLMB12Transducer,uss/HooimeijerLMSV11},
runtime behavior monitoring \cite{osdi/YaseenABCL20}, automated program
transformation \cite{pldi/HuD17}, and finally SMT solving for the unicode theory
of strings (e.g. see \cite{pacmpl/ChenFHHHKLRW22,CHL+19}).
%Furthermore, numerous studies have demonstrated the broad applicability of SFTs across diverse domains. The work of \cite{VeanesHLMB12Transducer} showcases SFTs in security-critical applications, particularly for cross-site scripting (XSS) prevention. \cite{uss/HooimeijerLMSV11} extends this security focus by applying SFTs to web application sanitizer analysis. In system verification, \cite{osdi/YaseenABCL20} employs SFTs for runtime behavior monitoring, while \cite{pldi/HuD17} demonstrates their utility in automated program transformation through systematic inversion techniques.
%This symbolic approach not only provides a more succinct representation but also supports infinite alphabets, thereby extending the expressive capabilities of FAs and FTs.

@@

Despite these, existing verified implementations for string analysis do not
handle the following indispensable string operations for analysis of web
applications (e.g. see
\cite{DBLP:conf/popl/LinB16,Kern,Berkeley-JavaScript,systematic-transduction,uss/HooimeijerLMSV11}):
\emph{string transductions} and \emph{replaceall} operators. In particular, 
string transductions are used frequently in web applications (e.g. for
sanitization, as well as implicitly applied transductions, for instance
through \texttt{innerHTML}) and are well-known to be critical for analyzing XSS
vulnerabilities for web applications
\cite{Berkeley-JavaScript,systematic-transduction,Kern,uss/HooimeijerLMSV11,DBLP:conf/popl/LinB16}. In particular, SMT-LIB string constraints that 
arise from such applications require the \emph{replaceall} operator, which is currently not handled by any existing verified
implementation, as far as we know. This paper tackles the formalization of SFA/SFT and
their associated algorithms, as well as applications to analysis of sanitizers
and verified solver for string constraints. 
%\textcolor{red}{Updated up to here
%so far}
